---
title: "FIALLOS"
author: "Andres Fiallos"
format: html
---

#Question 1

Load the data set

```{r}
here::i_am("lab-grades.Rproj")
library(here)
library(vroom)
library(dplyr)

data <- vroom(here("data.csv"))
```

#Question 2

Give the number of grades in the data set directly in the text of your quarto file, in a sentence of the form “The data set contains xxx grades.” where xxx is replaced by the number of grades. This must be computed from the data set.

**Answer:** 
The data set contains `r NROW(data)` grades

#Question 3

Use distinct() compute the number of students on the data set and report the value directly
in the text as in the previous question.

```{r}
unique <- distinct(data, id)
```

**Answer:** 
The number of students in the data set is `r NROW(unique)`. 

#Question 4

Create a students data frame that contains one row per student and two variables, id and
group that gives the assignment of each student to their group. Make sure that each student
appears on only once in the data frame. Include a short extract of the data frame in the quarto
rendering.

```{r}
students <- data |> distinct(id,.keep_all = T) |> select(id,group)

students |>
slice_tail(n = 5) |>
knitr::kable()
```

#Question 5

Use a graphical representation to display the number of students per group.

```{r}
library(ggplot2)
check <- students |> summarise( n = n()) 

ggplot(students |> summarise( n = n(), .by= group), aes(x = group, y = n))+
  geom_bar(stat = "identity") +  
  theme_minimal() +  
  labs(x = "Group", y = "ID", title = "Number of students per group")  

```

#Question 6

Compute the average of all the grades in Shamanism and Spiritual Practices in each group and
display graphically this average as a function of the group. It is recommend to use geom_col()
for this task (read the documentation!).

```{r}
q6 <- data |> filter(course == "Shamanism and Spiritual Practices")

table(data$semester)
table(q6$semester)

q6 <- q6 |> summarise(avg_grade = mean(grade), .by = group)

ggplot(q6, aes(x = group, y = avg_grade))+
  geom_col() +  
  theme_minimal() +  
  labs(x = "Group", y = "Average grade", title = "Average grade in Shamanisn and Spiritual Practices per group")  


```

# Question 7
Compare graphically the distribution of the grades of the 2 semesters.
```{r}
q7 <- data |> summarise(avg_grade = mean(grade), .by = semester)

ggplot(q7, aes(x = semester, y = avg_grade))+
  geom_col() +  
  theme_minimal() +  
  labs(x = "Semester", y = "Average grade", title = "Average grade by semester")  

```

#Question 8
Compute the number of grades per student and include in your quarto rendering an extract of
the resulting data frame. Make sure to keep in the data frame the id of the students but also
their group. Include in the text a markdown table with the minimum, maximum, average and
median number of grades per student.

```{r}

q8 <- data |> group_by(id,group) |> summarise(n_grades = n()) |> ungroup()

summary(q8$n_grades)
```


#Question 9
Create a data frame that gives for each student their id, their group and the number of grades
they obtained in Astronomy and Celestial Navigation and include in the quarto rendering a
small extract of the result.

```{r}
q9 <- data |> filter(course == "Astronomy and Celestial Navigation") |> group_by(id,group) |> summarise(n_grades = n()) |> ungroup() |> mutate(course = "Astronomy and Celestial Navigation")

q9 |>
slice_tail(n = 5) |>
knitr::kable()
```


#Question 10
Compute from the previous data frame the distribution of the number of grades, that is for each
number of grades (e.g. 10) the number of students who have exactly this number of grades in
Astronomy and Celestial Navigation. Represent graphically the results.

```{r}

```

#Question 11
Using a graphical representation to study whether the number of grades per student in Astron-
omy and Celestial Navigation depends on the group.
