---
title: "FIALLOS"
author: "Andres Fiallos"
format: html
---

#Question 1

Load the data set

```{r}
here::i_am("lab-grades.Rproj")
library(here)
library(vroom)
library(dplyr)

data <- vroom(here("data.csv"))
```

#Question 2

Give the number of grades in the data set directly in the text of your quarto file, in a sentence of the form “The data set contains xxx grades.” where xxx is replaced by the number of grades. This must be computed from the data set.

**Answer:** 
The data set contains `r NROW(data)` grades

#Question 3

Use distinct() compute the number of students on the data set and report the value directly
in the text as in the previous question.

```{r}
unique <- distinct(data, id)
```

**Answer:** 
The number of students in the data set is `r NROW(unique)`. 

#Question 4

Create a students data frame that contains one row per student and two variables, id and
group that gives the assignment of each student to their group. Make sure that each student
appears on only once in the data frame. Include a short extract of the data frame in the quarto
rendering.

```{r}
students <- data |> distinct(id,.keep_all = T) |> select(id,group)

students |>
slice_tail(n = 5) |>
knitr::kable()
```

#Question 5

Use a graphical representation to display the number of students per group.

```{r}
library(ggplot2)
check <- students |> summarise( n = n()) 

ggplot(students |> summarise( n = n(), .by= group), aes(x = group, y = n))+
  geom_bar(stat = "identity") +  
  theme_minimal() +  
  labs(x = "Group", y = "ID", title = "Number of students per group")  

```

#Question 6

Compute the average of all the grades in Shamanism and Spiritual Practices in each group and
display graphically this average as a function of the group. It is recommend to use geom_col()
for this task (read the documentation!).

```{r}
q6 <- data |> filter(course == "Shamanism and Spiritual Practices")

table(data$semester)
table(q6$semester)

q6 <- q6 |> summarise(avg_grade = mean(grade), .by = group)

ggplot(q6, aes(x = group, y = avg_grade))+
  geom_col() +  
  theme_minimal() +  
  labs(x = "Group", y = "Average grade", title = "Average grade in Shamanisn and Spiritual Practices per group")  


```

# Question 7
Compare graphically the distribution of the grades of the 2 semesters.
```{r}
q7 <- data |> summarise(avg_grade = mean(grade), .by = semester)

ggplot(q7, aes(x = semester, y = avg_grade))+
  geom_col() +  
  theme_minimal() +  
  labs(x = "Semester", y = "Average grade", title = "Average grade by semester")  

```

#Question 8
Compute the number of grades per student and include in your quarto rendering an extract of
the resulting data frame. Make sure to keep in the data frame the id of the students but also
their group. Include in the text a markdown table with the minimum, maximum, average and
median number of grades per student.

```{r}

q8 <- data |> group_by(id,group) |> summarise(n_grades = n()) |> ungroup()

summary(q8$n_grades)
```


#Question 9
Create a data frame that gives for each student their id, their group and the number of grades
they obtained in Astronomy and Celestial Navigation and include in the quarto rendering a
small extract of the result.

```{r}
q9 <- data |> filter(course == "Astronomy and Celestial Navigation") |> group_by(id,group) |> summarise(n_grades = n()) |> ungroup() |> mutate(course = "Astronomy and Celestial Navigation")

q9 |>
slice_tail(n = 5) |>
knitr::kable()
```


#Question 10
Compute from the previous data frame the distribution of the number of grades, that is for each
number of grades (e.g. 10) the number of students who have exactly this number of grades in
Astronomy and Celestial Navigation. Represent graphically the results.

```{r}
table(q9$n_grades)
q10 <- q9 |> group_by(n_grades) |> summarise(n_students = n()) |> ungroup()

ggplot(q10, aes(x = n_grades, y = n_students))+
  geom_col() +  
  theme_minimal() +  
  labs(x = "Number of grades", y = "Number of students", title = "Number of students by number of grades", subtitle = "Astronomy and Celestial Navigation" )  

```

#Question 11
Using a graphical representation to study whether the number of grades per student in Astron-
omy and Celestial Navigation depends on the group.

```{r}
q11 <- q9 |> group_by(group, n_grades) |> summarise(n_students = n()) |> ungroup()

ggplot(q11, aes(x = n_grades, y = n_students))+
  geom_col() +  
  theme_minimal() + 
  facet_wrap(~group)
  labs(x = "Number of grades", y = "Number of students" , title = "Number of students by number of grades and group", subtitle = "Astronomy and Celestial Navigation" )  
```
#Question 12

Create a data frame that gives for each student their id, their group and the average of grades
they obtained in each course. Using an adapted pivoting method, create a new data frame
with one row per student and 12 columns: one for the id, one for the group and one per course.
Include in the quarto rendering a small extract of the data frame with the id and group columns
and with two of the course columns. 

```{r}
q12 <- data |>  group_by(id,group,course) |> summarise(avg_grades = mean(grade)) |> ungroup() 

library(tidyr)
q12 <- q12 |>
  pivot_wider(id_cols = c(id, group),
              names_from = course,
              values_from = avg_grades)
q12 |> 
  select(1:4) |>
  slice_tail(n = 5) |>
  knitr::kable()

```


#Question 13
Show the average grades in Environmental Stewardship as a function of the average grades in
Warfare and Diplomacy. Make sure to maximise the readability of the proposed representation.

```{r}
ggplot(q12, aes(x = `Environmental Stewardship`, y = `Warfare and Diplomacy`))+
  geom_point() +  
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  theme_minimal() + 
  labs(x = "Avg grade in Environmental Stewardship", y = "Avg grade in Warfare and Diplomacy" , title = "Environmental Stewardship ~ Warfare and Diplomacy" )  

```


#Question 14
The cor() function computes the correlation coeﬀicient between two vectors. It can be used as
a summary function in dplyr. Using it, compute the correlation between the average grades in
Language and Linguistics and the average grades in Astronomy and Celestial Navigation group
by group.

```{r}
q14 <- q12 |>  group_by(group) |> summarise(correlation = cor(`Language and Linguistics`,`Astronomy and Celestial Navigation`)) |> ungroup() 

q14 |> 
  slice_tail(n = 10) |>
  knitr::kable()
```


#Question 15
Display the average grades in Language and Linguistics as a function the average grades in
Astronomy and Celestial Navigation for the students of the group in which those grades are the
most correlated (positively or negatively).

```{r}
q15 <- q14 |> 
  mutate(correlation_max = max(abs(correlation), na.rm = TRUE)) |> filter(correlation_max == abs(correlation))

ggplot(q12 |> filter(group == 12), aes(x = `Language and Linguistics`, y = `Astronomy and Celestial Navigation`))+
  geom_point() +  
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  theme_minimal() + 
  labs(x = "Avg grade in Environmental Stewardship", y = "Avg grade in Warfare and Diplomacy" , title = "Environmental Stewardship ~ Warfare and Diplomacy", subtitle = "Group 12: max correlation between grades")  

```


#Question 16
Let us assume that the final grade of a student is the average of the averages of their grades
for each course. Create a data frame with three columns, id, group and final grade based on
this definition for the last column. Sort the data frame in decrease order of final grade and
include in the quarto rendering its first five rows.

```{r}

```


#Question 17
Find a way to study differences in final grades between groups.


#Question 18
To pass the year, a student must fulfil the following conditions:
• have no average grade in a course lower than 5;
• have an average grade in each semester larger or equal to 10 (the average in a semester is
simply the average of the average grades of the courses in the semester).
Create a data frame that gives for each student their id, their group, their final grade (as
defined before) and a pass variable equal to TRUE if the student pass the year (and FALSE if they
do not).

#Question 19
Compute and display the number of students who do not pass and yet have a final grade larger
or equal to 10.

#Question 20
Compute the pass rate per group and represent it graphically.

